Will Kamala Harris will win the 2024 Presidential election

### 2024-11-04 paper/paper.qmd
weakness and next steps

## Weaknesses and next steps

Weaknesses and next steps should also be included.

>>>>

## Limitations and Weaknesses
- nuemric_grade couldve been used to weigh pollster results, for accuracy 
- lack of real time adjustments 
- less data to use becuase we are only considering data since Harris's declaration as a candidate 
- limited scope of variables (demographic changes, economic conditions, and recent events, are not included)
- some ambiguity of results, nothing to compare to

## Next steps

- use historical data from past elections to identify strong voting patterns 
- generate confidence intervals 
- integrate more context, and more vairables : Future studies could examine how state-level socioeconomic and political factors, such as unemployment rates, healthcare concerns, or local election issues, might influence voter preferences in each swing state. This would add depth to the model and align predictions more closely with real-world factors.
